Suppl. Figure 1. Bacterial abundance across datasets

### 2022-02-10 reports/rmarkdown/manuscript/Suppl.Figure1.Rmd
Save pdf image to common folder

---
title: "Suppl. Figure 1. Bacterial abundance across datasets"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

@@

```{r Bacterial abundance, echo = FALSE, eval = TRUE,  fig.asp=.5}
par(mar=c(6,2.5,0,0)) #b,l,t,r

top_all <- lapply( datasets_all_samples[2:3] , function(x){
   sort(apply(x,1,var),decreasing = T)[1:20]} )
top <- unique( sub( ".*[.]" , "" , names(unlist(top_all)) ) )

@@

temp <- factor(top, levels=top)
violist(data = x[,colnames(x)%in%top],
        genes = rownames(x),
        clustering = factor( colnames(x)[colnames(x)%in%top],levels = top) ,
        srt=45, cex.axis=0.7, pt.cex=0.2,
        transparency = 50,col = pal)
```

>>>>

---
title: "Suppl. Figure 1. Bacterial abundance across datasets"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
```

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

@@

```{r Suppl.Fig.1 Bacterial_abundance, echo = FALSE, eval = TRUE,  fig.asp=.5}
top_all <- lapply( datasets_all_samples[2:3] , function(x){
   sort(apply(x,1,var),decreasing = T)[1:20]} )
top <- unique( sub( ".*[.]" , "" , names(unlist(top_all)) ) )

@@

###################################
# BACTERIAL ABUNDANCE IN DATASETS #
###################################
par(mar=c(6,2.5,0,0)) #b,l,t,r
violist(data = x[,colnames(x)%in%top],
        genes = rownames(x),
        clustering = factor( colnames(x)[colnames(x)%in%top],levels = top) ,
        srt=45, cex.axis=0.7, pt.cex=0.2,
        transparency = 50,col = pal)
```
